Parenting observation lexical diversity - Exp 1

### 2019-02-11 paper/cogsci2019/cogsci2019.Rmd
revised intro and added demo and reliability info

## Guided Play Scaffolds Learning
Children's early play behaviors are often assisted by more skilled and knowledgeable play partners such as their caregivers and older siblings [@Kaye1970]. 
Under such expert guidance, children are encouraged and motivated to engage in more advanced play, undertaking explorations that push the boundaries of what they would be able to do unaided [@Vygotsky1978].
These tutorial interactions have been shown to be an important component of child development [@Wood1976].
Thus, with the knowledge of both play and tutorial interactions, guided play, which consists of both active and enjoyable activities as well as close guidance of adults [@Hirsh2008]
have drawn researchers' interest. 
Weisberg showed that, with preschoolers, guided play scaffolds the environment while still allowing children to maintain a large degree of control, 
and it outperforms direct-instruction approaches in encouraging a variety of positive academic outcomes [@Weisberg2013].
Massey specifically showed that guided play could facilitate children's vocabulary and comprehensive language development and subsequent literacy skills [@Massey2013].

## Improving Parenting Practices and Language Use
Thus, including guided play in parenting practices early on is important and should help with children's later performances. Suskind did a parent-directed home-visiting intervention experiment in 2015, 
and found that parents in experimental group have greater knowledge of language development and this effect sustained after the experiment is done. 
However, more interactive outcomes, like parent word type and token numbers, child word types, conversational turn counts and child vocalization counts, 
increased during the home-visiting but did not sustain after four months of intervention (there are more detailed sustainibility differences of these measure. should I make it more clear?) [@Suskind2015].
That changes did not sustain could be due to the intervention itself,
or could merely be that home-visiting is not sustainable enough for parents to easily and constantly get parenting advice. 
Thus, new methods of delivering parenting advice should be considered.

## Effectiveness of Digital Delivery
Digitally-delivered methods could address some logistic barriers to face-to-face delivery methods. 
Breitenstein reviewed 11 studies on them and showed good promise for the efficacy of interventions using digitally-delivered methods [@Breitenstein2014].
However, the parent and child outcomes assessed in the review (e.g.infant positive behaviors, satisfaction, emotional symptoms etc.) did not address the nature or quality of parent-infant interactions at a detailed level,
like if the interventions lead to children paying more attention, or vocabulary changes in parents' language usages. 
Although digitally-delivered ac-tivities are designed to promote learning and cognitive devel-opment, it is unclear how they might affect these dimensions of parent-child interactions.
Thus, we want to conduct this experiment to explore if and how digital scaffolding of activities affect the social and linguistic characteristics of parent-child ineractions.
The quality of parent-child interactions can be measured by both the social engagement of parents (e.g., joint attention to objects in the environment)[@Bigelow2004] and the quality of language (e.g., vocabulary diversity) [@Malvern2004].

@@

lmer_data <- d %>%
  filter(!is.na(AA), !is.na(EL), !is.na(RR))%>%
  mutate(condition = factor(condition), 
         MTLD = as.numeric(MTLD),
         EL = as.numeric(langcog::scale(EL, scale=FALSE)),
         AA = as.numeric(langcog::scale(AA, scale=FALSE)),
         RR = as.numeric(langcog::scale(RR, scale=FALSE)),
         age = as.numeric(langcog::scale(age, scale=FALSE)),
         gender = as.factor(gender),
         video = as.factor(video))
```

### Participants. 
`r nrow(d)` infants aged 6-24 months and their parents participated in a museum in northern California. 
We included infants who were exposed to English at least 50 percent of the time or who were exposed less but whose participating parent reported that they primarily speak English with their child at home.
*INCLUDE FULL DEMOGRAPHIC INFO*

@@

Participants were randomly assigned to either the Activity *Video* condition or the No-Video *Control* condition. 
Participants in the Activity Video condition were assigned to one of the two videos available for their child's age group. 
The No-Video Control condition was yoked to the Activity Video condition such that for every participant in the Activity Video condition who saw a particular video and received the associated props, a participant in the No-Video Control condition received the same props but did not watch the corresponding video.
Parents also completed the Parenting Attitudes Questionnaire (PAQ). 
The PAQ measures parents' attitudes about parenting and child development along three dimensions: rules and respect, early learning, and affection and attachment.

@@

### Joint Attention Coding Procedure.
The video of each session was manually coded for episodes of joint attention using the Datavyu software. 
The video taken at floor level was coded by default, but the other video was referred to if the participants were not visible or if there was a technological error with the first camera. 
For each participant we coded for episodes of coordinated joint attention, episodes of passive joint attention, and parental bids for joint attention. 
We defined parental bids for joint attention as any attempt to initiate joint attention (i.e label, point, or otherwise draw attention to an object) that does not result in passive or coordinated joint attention. 
If more than 3 seconds elapsed between bids, they were coded as separate attempts. 
An episode of joint attention was considered passive if both participants visually focused on an object for a minimum of 3 seconds but the child did not acknowledge the parent. 
If either participant looked away from the object for less than 3 seconds and then returned to the same object it was considered part of the same period of joint attention. 
Episodes joint attention were considered coordinated if  both participants visually focused on an object for a minimum of 3 seconds and at some point in the interaction the child indicated awareness of interaction with some overt behavior toward the parent. 
This could be looks to the parent's face, gestures, vocalizations, or turn-taking. 
If either participant looked away for less than 3 seconds and then returned to the same object, it was coded as part of the same period of joint attention. 
A second coder independently coded a third of the videos (i.e., 20 of the 60 videos, approximately equally distributed across ages) to establish reliability. *REPORT RELIABILITY*

@@

### Materials. 
The design of Experiment 2 was similar to that of Experiment 1, except that instead of a No-Video control condition, parents instead watched a video that was generally related to child development research, but did not give any specific instructions about how to interact with infants or children. 
This was to control for the possibility that differences in language output and joint attention in Experiment 1 could be due to simply cuing parents to think about infants' learning and cognitive development. 
The videos presented in the Control Video condition were media clips (available on YouTube) of developmental psychologists explaining their research interleaved with footage of infants or toddlers engaged in developmental research studies. 
Thus, the content of the videos superficially matched those in the Activity Video condition, but did not suggest any particular activities.
The videos were trimmed to approximately match the average video length in the Activity Video condition (2 minutes ??).

>>>>

## Guided Play Scaffolds Learning
Children's early play behaviors are often assisted by more skilled and knowledgeable play partners such as their caregivers and older siblings [@Kaye1970]. 
Under such expert guidance, children are encouraged and motivated to engage in more advanced play, undertaking explorations that push the boundaries of what they would be able to do unaided [@Vygotsky1980].
These tutorial interactions have been shown to be important components of child development [@Wood1976].
Thus, with the knowledge of both play and tutorial interactions, guided play, which consists of both active and enjoyable activities as well as close guidance of adults [@Hirsh2008]
has drawn researchers' interest. 
A study on preschoolers by Weisberg showed that guided play scaffolds the environment while still allowing children to maintain a large degree of control, 
and it outperforms direct-instruction approaches in encouraging a variety of positive academic outcomes [@Weisberg2013].
Another study by Massey specifically found that guided play could facilitate children's vocabulary and comprehensive language development and subsequent literacy skills [@Massey2013].

## Improving Parenting Practices and Language Use
Thus, including guided play in parenting practices early on is crucial and will help with children's later performances in academic and social situations. 
To intervene in parenting practices, Suskind and others did a parent-directed home-visiting intervention experiment in 2015 for children of low socioeconomic status.
They showed that parents in experimental group have greater knowledge of language development and this effect sustained four months after the intervention. 
However, more interactive outcomes, like adult word tokens, conversational turn counts, and child vocalization counts, 
though increased significantly during the experiment,
did not sustain after the intervention [@Suskind2015].
That changes did not sustain could be due to the intervention itself,
or could merely be that the methods of home-visiting is not sustainable enough for parents to easily and constantly get parenting advice.
Thus, new methods of delivering parenting advice should be considered.

## Effectiveness of Digital Delivery
With the development of technology, digitally-delivered methods could address some logistic barriers to face-to-face delivery methods. 
Breitenstein has reviewed 11 studies on them and showed good promise for the efficacy of interventions using digitally-delivered methods [@Breitenstein2014].
However, the parent and child outcomes assessed in the review (e.g.infant positive behaviors, satisfaction, emotional symptoms etc.) did not address the nature or quality of parent-infant interactions at a detailed level,
like if the interventions lead to children paying more attention, or vocabulary changes in parents' language usages. 
Although digitally-delivered ac-tivities are designed to promote learning and cognitive devel-opment, it is unclear how they might affect these dimensions of parent-child interactions.
Thus, we want to conduct this experiment to explore if and how digital scaffolding of activities affect the social and linguistic characteristics of parent-child ineractions.
The quality of parent-child interactions can be measured by both the social engagement of parents (e.g., joint attention to objects in the environment)[@Bigelow2004] and the quality of language (e.g., vocabulary diversity) [@Malvern2004].

@@

lmer_data <- d %>%
  filter(!is.na(AA), !is.na(EL), !is.na(RR))%>%
  mutate(condition = factor(condition), 
         MTLD = as.numeric(MTLD),
         EL = as.numeric(langcog::scale(EL, scale=FALSE)),
         AA = as.numeric(langcog::scale(AA, scale=FALSE)),
         RR = as.numeric(langcog::scale(RR, scale=FALSE)),
         age = as.numeric(langcog::scale(age, scale=FALSE)),
         gender = as.factor(gender),
         video = as.factor(video))

a <- d$gender == "F"
length(a[a == TRUE])

### Participants. 
`r nrow(d)` infants  (F=42, M=18) aged 6-24 months (20 6-11.9 month-olds, 20 12-17.9 month-olds, and 20 18-24 month-olds) and their parents participated in a museum in northern California. 
We included infants who were exposed to English at least 50 percent of the time (n= 58) or who were exposed less but whose participating parent reported that they primarily speak English with their child at home (n = 2). Sixty-one% of participants (n=37) had been exposed to 2 or more languages as indicated by their parent. Parents identified their children as White (n=25), Asian (n=11), African American/Black (n=2), Biracial (n=12), other (n=5), or declined to state (n=5). Fifteen parents reported their child was of Hispanic origin. Parents tended to be highly educated, with a highest level of education reported as high school (n = 5), some college (n = 6), four-year college (n = 14), some graduate school (n = 1), completed graduate school (n = 28) or declined to state (n=6).

@@

Participants were randomly assigned to either the *Video* condition or the *Control* condition. 
Participants in the Activity Video condition were assigned to one of the two videos available for their child's age group. 
The No-Video Control condition was yoked to the Activity Video condition such that for every participant in the Activity Video condition who saw a particular video and received the associated props, a participant in the No-Video Control condition received the same props but did not watch the corresponding video.
Parents also completed the Parenting Attitudes Questionnaire (PAQ). 
The PAQ measures parents' attitudes about parenting and child development along three dimensions: rules and respect, early learning, and affection and attachment.

@@

### Joint Attention Coding Procedure.
The video of each session was manually coded for episodes of joint attention using the Datavyu software. 
The video taken at floor level was coded by default, but the other video was referred to if the participants were not visible or if there was a technological error with the first camera. 
For each participant we coded for episodes of coordinated joint attention, episodes of passive joint attention, and parental bids for joint attention. 
We defined parental bids for joint attention as any attempt to initiate joint attention (i.e label, point, or otherwise draw attention to an object) that does not result in passive or coordinated joint attention. 
If more than 3 seconds elapsed between bids, they were coded as separate attempts. 
An episode of joint attention was considered passive if both participants visually focused on an object for a minimum of 3 seconds but the child did not acknowledge the parent. 
If either participant looked away from the object for less than 3 seconds and then returned to the same object it was considered part of the same period of joint attention. 
Episodes joint attention were considered coordinated if  both participants visually focused on an object for a minimum of 3 seconds and at some point in the interaction the child indicated awareness of interaction with some overt behavior toward the parent. 
This could be looks to the parent's face, gestures, vocalizations, or turn-taking. 
If either participant looked away for less than 3 seconds and then returned to the same object, it was coded as part of the same period of joint attention. 
A second coder independently coded a third of the videos (i.e., 20 of the 60 videos, approximately equally distributed across ages) to establish reliability. The two coders achieved reliability with ICC = 0.80 with 95% confident interval = 0.57-0.92 (p<0.05) for number of parent bids; ICC = 0.20 with 95% confident interval = -0.26-0.58 for number of passive joint attention established; ICC = 0.66 with 95% confident interval = 0.32-0.85 (p<0.05) for number of coordinated joint attention established; ICC = 0.24 with 95% confident interval = -0.21-0.61 for length of passive joint attention, and ICC = 0.62 with 95% confident interval = 0.27-0.83 (p<0.05) for length of passive joint attention.

@@

### Materials. 
The design of Experiment 2 was similar to that of Experiment 1, except that instead of a No-Video control condition, parents instead watched a video that was generally related to child development research, but did not give any specific instructions about how to interact with infants or children. 
This was to control for the possibility that differences in language output and joint attention in Experiment 1 could be due to simply cuing parents to think about infants' learning and cognitive development. 
The videos presented in the Control Video condition were media clips (available on YouTube) of developmental psychologists explaining their research interleaved with footage of infants or toddlers engaged in developmental research studies. 
Thus, the content of the videos superficially matched those in the Activity Video condition, but did not suggest any particular activities.
The videos were trimmed to approximately match the average video length in the Activity Video condition around 1.5 minutes.

### 2019-02-11 paper/cogsci2019/cogsci2019.tex
revised intro and added demo and reliability info

Children's early play behaviors are often assisted by more skilled and
knowledgeable play partners such as their caregivers and older siblings
(Kaye, 1970). Under such expert guidance, children are encouraged and
motivated to engage in more advanced play, undertaking explorations that
push the boundaries of what they would be able to do unaided (Vygotsky,
197X). These tutorial interactions have been shown to be a ``a crucial
feature of infancy and childhood'' (Wood, 1970). Thus, with the
knowledge of both play and tutorial interactions, guided play, ``where
children actively engage in pleasurable and seemingly spontaneous
activities under the direction of adults'' (Hirsh-Pasek, 2008), have
drawn researchers' interest. Weisberg showed that, with preschoolers,
guided play scaffolds the environment while still allowing children to
maintain a large degree of control, and it outperforms
direct-instruction approaches in encouraging a variety of positive
academic outcomes (Weisberg, Hirsh-Pasek and Golinkoff, 2013). Massey
specifically showed that guided play could facilitate children's
vocabulary and comprehensive language development and subsequent
literacy skills (Massey, 2013).

@@

(early interventions on parenting practices can help children's
outcomes) Thus, including guided play in parenting practices early on is
important and should help with children's later performances. Suskind
did a parent-directed home-visiting intervention experiment in 2015, and
found that parents in experimental group have greater knowledge of
language development and this effect sustained after the experiment is
done. However, more interactive outcomes, like parent word type and
token numbers, child word types, conversational turn counts and child
vocalization counts, increased during the home-visiting but did not
sustain after four months of intervention (there are more detailed
sustainibility differences of these measure. should I make it more
clear?) (D. L. Suskind et al., 2015). The fact that changes did not
sustain could be due to the intervention itself, or could merely be that
home-visiting is not sustainable enough for parents to easily and
constantly get parenting advice.

@@

(apps are an easy way to deliver curated, age-appropriate parenting
advice --- but can we measure an influence on parent's language? and do
the interventions lead to children paying more attention?)

Digitally-delivered methods could address some logistic barriers to
face-to-face delivery methods. Bretenstein reviewed 11 studies on them
and showed good promise for the efficacy of interventions using
digitally-delivered methods. However, the parent and child outcomes
assessed in the review (e.g.infant positive behaviors, satisfaction,
emotional symptoms etc.) did not address the nature or quality of
parent-infant interactions at a detailed level, like if the
interventions lead to children paying more attention, or vocabulary
changes in parents' language usages. Thus, we want to conduct this
experiment to explore if and how digital scaffolding of activities
affect the social and linguistic characteristics of parent-child
ineractions.

The quality of parent-child interactions can be measured by both the
social engagement of parents (e.g., joint attention to objects in the
environment) and the quality of language (e.g., vocabulary diversity).
Although digitally-delivered activities are designed to promote learning
and cognitive development, it is unclear how they might affect these
dimensions of parent-child interactions. How does digital scaffolding of
activities affect the social and linguistic characteristics of parents'
speech to their children?

@@

@@

59 infants aged 6-24 months and their parents participated in a museum
in northern California. We included infants who were exposed to English
at least 50 percent of the time or who were exposed less but whose
participating parent reported that they primarily speak English with
their child at home. \emph{INCLUDE FULL DEMOGRAPHIC INFO}

@@

Participants were randomly assigned to either the Activity \emph{Video}
condition or the No-Video \emph{Control} condition. Participants in the
Activity Video condition were assigned to one of the two videos
available for their child's age group. The No-Video Control condition
was yoked to the Activity Video condition such that for every
participant in the Activity Video condition who saw a particular video
and received the associated props, a participant in the No-Video Control
condition received the same props but did not watch the corresponding
video. Parents also completed the Parenting Attitudes Questionnaire
(PAQ). The PAQ measures parents' attitudes about parenting and child
development along three dimensions: rules and respect, early learning,
and affection and attachment.

@@

The video of each session was manually coded for episodes of joint
attention using the Datavyu software. The video taken at floor level was
coded by default, but the other video was referred to if the
participants were not visible or if there was a technological error with
the first camera. For each participant we coded for episodes of
coordinated joint attention, episodes of passive joint attention, and
parental bids for joint attention. We defined parental bids for joint
attention as any attempt to initiate joint attention (i.e label, point,
or otherwise draw attention to an object) that does not result in
passive or coordinated joint attention. If more than 3 seconds elapsed
between bids, they were coded as separate attempts. An episode of joint
attention was considered passive if both participants visually focused
on an object for a minimum of 3 seconds but the child did not
acknowledge the parent. If either participant looked away from the
object for less than 3 seconds and then returned to the same object it
was considered part of the same period of joint attention. Episodes
joint attention were considered coordinated if both participants
visually focused on an object for a minimum of 3 seconds and at some
point in the interaction the child indicated awareness of interaction
with some overt behavior toward the parent. This could be looks to the
parent's face, gestures, vocalizations, or turn-taking. If either
participant looked away for less than 3 seconds and then returned to the
same object, it was coded as part of the same period of joint attention.
A second coder independently coded a third of the videos (i.e., 20 of
the 60 videos, approximately equally distributed across ages) to
establish reliability. \emph{REPORT RELIABILITY}

@@

The design of Experiment 2 was similar to that of Experiment 1, except
that instead of a No-Video control condition, parents instead watched a
video that was generally related to child development research, but did
not give any specific instructions about how to interact with infants or
children. This was to control for the possibility that differences in
language output and joint attention in Experiment 1 could be due to
simply cuing parents to think about infants' learning and cognitive
development. The videos presented in the Control Video condition were
media clips (available on YouTube) of developmental psychologists
explaining their research interleaved with footage of infants or
toddlers engaged in developmental research studies. Thus, the content of
the videos superficially matched those in the Activity Video condition,
but did not suggest any particular activities. The videos were trimmed
to approximately match the average video length in the Activity Video
condition (2 minutes ??).

@@

\hypertarget{refs}{}
\hypertarget{ref-Hart1995}{}
Hart, B., \& Risley, T. R. (1995). \emph{Meaningful differences in the
everyday experience of young american children}. Baltimore, MD: Brookes.

@@

@@

>>>>

Children's early play behaviors are often assisted by more skilled and
knowledgeable play partners such as their caregivers and older siblings
(Kaye, 1970). Under such expert guidance, children are encouraged and
motivated to engage in more advanced play, undertaking explorations that
push the boundaries of what they would be able to do unaided (Vygotsky,
1980). These tutorial interactions have been shown to be important
components of child development (Wood, Bruner, \& Ross, 1976). Thus,
with the knowledge of both play and tutorial interactions, guided play,
which consists of both active and enjoyable activities as well as close
guidance of adults (Hirsh-Pasek \& Golinkoff, 2008) has drawn
researchers' interest. A study on preschoolers by Weisberg showed that
guided play scaffolds the environment while still allowing children to
maintain a large degree of control, and it outperforms
direct-instruction approaches in encouraging a variety of positive
academic outcomes (Weisberg, Hirsh-Pasek, \& Golinkoff, 2013). Another
study by Massey specifically found that guided play could facilitate
children's vocabulary and comprehensive language development and
subsequent literacy skills (Massey, 2013).

@@

Thus, including guided play in parenting practices early on is crucial
and will help with children's later performances in academic and social
situations. To intervene in parenting practices, Suskind and others did
a parent-directed home-visiting intervention experiment in 2015 for
children of low socioeconomic status. They showed that parents in
experimental group have greater knowledge of language development and
this effect sustained four months after the intervention. However, more
interactive outcomes, like adult word tokens, conversational turn
counts, and child vocalization counts, though increased significantly
during the experiment, did not sustain after the intervention (D. L.
Suskind et al., 2015). That changes did not sustain could be due to the
intervention itself, or could merely be that the methods of
home-visiting is not sustainable enough for parents to easily and
constantly get parenting advice. Thus, new methods of delivering
parenting advice should be considered.

@@

With the development of technology, digitally-delivered methods could
address some logistic barriers to face-to-face delivery methods.
Breitenstein has reviewed 11 studies on them and showed good promise for
the efficacy of interventions using digitally-delivered methods
(Breitenstein, Gross, \& Christophersen, 2014). However, the parent and
child outcomes assessed in the review (e.g.infant positive behaviors,
satisfaction, emotional symptoms etc.) did not address the nature or
quality of parent-infant interactions at a detailed level, like if the
interventions lead to children paying more attention, or vocabulary
changes in parents' language usages. Although digitally-delivered
ac-tivities are designed to promote learning and cognitive devel-opment,
it is unclear how they might affect these dimensions of parent-child
interactions. Thus, we want to conduct this experiment to explore if and
how digital scaffolding of activities affect the social and linguistic
characteristics of parent-child ineractions. The quality of parent-child
interactions can be measured by both the social engagement of parents
(e.g., joint attention to objects in the environment)(Bigelow, MacLean,
\& Proctor, 2004) and the quality of language (e.g., vocabulary
diversity) (Malvern, Richards, Chipere, \& Durán, 2004).

@@

\begin{CodeChunk}
\begin{CodeOutput}
[1] 45
\end{CodeOutput}
\end{CodeChunk}

@@

60 infants (F=42, M=18) aged 6-24 months (20 6-11.9 month-olds, 20
12-17.9 month-olds, and 20 18-24 month-olds) and their parents
participated in a museum in northern California. We included infants who
were exposed to English at least 50 percent of the time (n= 58) or who
were exposed less but whose participating parent reported that they
primarily speak English with their child at home (n = 2). Sixty-one\% of
participants (n=37) had been exposed to 2 or more languages as indicated
by their parent. Parents identified their children as White (n=25),
Asian (n=11), African American/Black (n=2), Biracial (n=12), other
(n=5), or declined to state (n=5). Fifteen parents reported their child
was of Hispanic origin. Parents tended to be highly educated, with a
highest level of education reported as high school (n = 5), some college
(n = 6), four-year college (n = 14), some graduate school (n = 1),
completed graduate school (n = 28) or declined to state (n=6).

@@

Participants were randomly assigned to either the \emph{Video} condition
or the \emph{Control} condition. Participants in the Activity Video
condition were assigned to one of the two videos available for their
child's age group. The No-Video Control condition was yoked to the
Activity Video condition such that for every participant in the Activity
Video condition who saw a particular video and received the associated
props, a participant in the No-Video Control condition received the same
props but did not watch the corresponding video. Parents also completed
the Parenting Attitudes Questionnaire (PAQ). The PAQ measures parents'
attitudes about parenting and child development along three dimensions:
rules and respect, early learning, and affection and attachment.

@@

The video of each session was manually coded for episodes of joint
attention using the Datavyu software. The video taken at floor level was
coded by default, but the other video was referred to if the
participants were not visible or if there was a technological error with
the first camera. For each participant we coded for episodes of
coordinated joint attention, episodes of passive joint attention, and
parental bids for joint attention. We defined parental bids for joint
attention as any attempt to initiate joint attention (i.e label, point,
or otherwise draw attention to an object) that does not result in
passive or coordinated joint attention. If more than 3 seconds elapsed
between bids, they were coded as separate attempts. An episode of joint
attention was considered passive if both participants visually focused
on an object for a minimum of 3 seconds but the child did not
acknowledge the parent. If either participant looked away from the
object for less than 3 seconds and then returned to the same object it
was considered part of the same period of joint attention. Episodes
joint attention were considered coordinated if both participants
visually focused on an object for a minimum of 3 seconds and at some
point in the interaction the child indicated awareness of interaction
with some overt behavior toward the parent. This could be looks to the
parent's face, gestures, vocalizations, or turn-taking. If either
participant looked away for less than 3 seconds and then returned to the
same object, it was coded as part of the same period of joint attention.
A second coder independently coded a third of the videos (i.e., 20 of
the 60 videos, approximately equally distributed across ages) to
establish reliability. The two coders achieved reliability with ICC =
0.80 with 95\% confident interval = 0.57-0.92 (p\textless{}0.05) for
number of parent bids; ICC = 0.20 with 95\% confident interval =
-0.26-0.58 for number of passive joint attention established; ICC = 0.66
with 95\% confident interval = 0.32-0.85 (p\textless{}0.05) for number
of coordinated joint attention established; ICC = 0.24 with 95\%
confident interval = -0.21-0.61 for length of passive joint attention,
and ICC = 0.62 with 95\% confident interval = 0.27-0.83
(p\textless{}0.05) for length of passive joint attention.

@@

The design of Experiment 2 was similar to that of Experiment 1, except
that instead of a No-Video control condition, parents instead watched a
video that was generally related to child development research, but did
not give any specific instructions about how to interact with infants or
children. This was to control for the possibility that differences in
language output and joint attention in Experiment 1 could be due to
simply cuing parents to think about infants' learning and cognitive
development. The videos presented in the Control Video condition were
media clips (available on YouTube) of developmental psychologists
explaining their research interleaved with footage of infants or
toddlers engaged in developmental research studies. Thus, the content of
the videos superficially matched those in the Activity Video condition,
but did not suggest any particular activities. The videos were trimmed
to approximately match the average video length in the Activity Video
condition around 1.5 minutes.

@@

\hypertarget{refs}{}
\hypertarget{ref-Bigelow2004}{}
Bigelow, A. E., MacLean, K., \& Proctor, J. (2004). The role of joint
attention in the development of infants' play with objects.
\emph{Developmental Science}, \emph{7}, 518--526.

\hypertarget{ref-Breitenstein2014}{}
Breitenstein, S. M., Gross, D., \& Christophersen, R. (2014). Digital
delivery methods of parenting training interventions: A systematic
review. \emph{Worldviews on Evidence-Based Nursing}, \emph{11},
168--176.

\hypertarget{ref-Hart1995}{}
Hart, B., \& Risley, T. R. (1995). \emph{Meaningful differences in the
everyday experience of young american children}. Baltimore, MD: Brookes.

@@

\hypertarget{ref-Hirsh2008}{}
Hirsh-Pasek, K., \& Golinkoff, R. M. (2008). Why play= learning.
\emph{Encyclopedia on Early Childhood Development}, 1--7.

\hypertarget{ref-Kaye1970}{}
Kaye, K. (1970). Mother-child instructional interaction.
\emph{Unpublished Doctoral Thesis, Department of Psychology, Harvard
University}.

\hypertarget{ref-Malvern2004}{}
Malvern, D., Richards, B. J., Chipere, N., \& Durán, P. (2004). Lexical
diversity and language development.

\hypertarget{ref-Massey2013}{}
Massey, S. L. (2013). From the reading rug to the play center: Enhancing
vocabulary and comprehensive language skills by connecting storybook
reading and guided play. \emph{Early Childhood Education Journal},
\emph{41}, 125--131.

@@

\hypertarget{ref-Vygotsky1980}{}
Vygotsky, L. S. (1980). Mind in society: The development of higher
psychological processes.

\hypertarget{ref-Weisberg2013}{}
Weisberg, D. S., Hirsh-Pasek, K., \& Golinkoff, R. M. (2013). Guided
play: Where curricular goals meet a playful pedagogy. \emph{Mind, Brain,
and Education}, \emph{7}, 104--112.

\hypertarget{ref-Wood1976}{}
Wood, D., Bruner, J. S., \& Ross, G. (1976). The role of tutoring in
problem solving. \emph{Journal of Child Psychology and Psychiatry},
\emph{17}, 89--100.

### 2019-02-11 parenting_obs_e1/parenting_obs_lexdiv.Rmd
revised intro and added demo and reliability info

```{r}
#data <- read.csv("lexdiv_data.csv", header=TRUE) # Emily's TTR calculation
data <- read.csv("MTLD_HDD.csv", header=TRUE) # Vivian's new TTR, MTLD, and HDD pipeline (generated by get_all_parent_speech.py)
data$SID = data$sid
data$sid = NULL
data$X = NULL
#dem <- read.csv("parenting_proj_emilyhembacher_demo2016.csv", header =TRUE) # anonymized demographics data
#dem_anon = dem[,c("SID","age","gender","ethnicity","english","parent_ed","num_lang","Exclude")]
#write.csv(dem_anon, file="anonymized_demographics_parenting_obs_e1.csv")
dem <- read.csv("anonymized_demographics_parenting_obs_e1.csv", header=T)
conditions <- read.csv("joint_attention/conditions.csv")
load("paq/paq_demo.RData") # do we use this?? GK: yes, see left_join on line 76

@@

data$SID <- stringr::str_replace(data$SID, "05116_05", "050116_05")
data$SID <- stringr::str_replace(data$SID, "05116_2", "050116_02")
```

>>>>

```{r}
#data <- read.csv("lexdiv_data.csv", header=TRUE) # Emily's TTR calculation
data <- read.csv("MTLD_HDD.csv", header=TRUE) # Vivian's new TTR, MTLD, and HDD pipeline (generated by get_all_parent_speech.py)
data$SID = data$sid
data$sid = NULL
data$X = NULL
#dem <- read.csv("parenting_proj_emilyhembacher_demo2016.csv", header =TRUE) # anonymized demographics data
#dem_anon = dem[,c("SID","age","gender","ethnicity","english","parent_ed","num_lang","Exclude")]
#write.csv(dem_anon, file="anonymized_demographics_parenting_obs_e1.csv")
dem <- read.csv("anonymized_demographics_parenting_obs_e1.csv", header=T)
conditions <- read.csv("joint_attention/conditions.csv")
load("paq/paq_demo.RData")

@@

data$SID <- stringr::str_replace(data$SID, "05116_05", "050116_05")
data$SID <- stringr::str_replace(data$SID, "05116_2", "050116_02")
data$SID <- stringr::str_replace(data$SID, "98470_111716_02", "111716_02")
```
